|

### 2019-06-28 inst/manuscript/manuscript.Rmd
Fix atcc analysis in manuscript.Rmd
Also:
 - Update figures affected by this fix

Issue:
 - Error in atcc analysis section
 - The proteins depicted in the 4 venn diagrams in Fig. 2A should
   include only proteins quantified in min 2/3 replicates of EV or WCL.
   However, some ATCC90028 and ATCC10231 proteins do not pass this
   statement.
 - Yeast and biofilm results unaffected.

Solution:
 - Change atcc analysis workflow from this method:
    - Filter, normalise, impute, split into ATCC90028 and ATCC10231,
      then perform separate DE analyses.
   to this method:
    - Filter, normalise, s

# filter for proteins identified in min 1/3 reps of EV
# define 'EV proteins'
y_ev <- filter_na(yeast_norm2, op = "<=", 
                  pat = "EV", val = 2)

# filter for proteins identified in min 1/3 reps of WCL
# define 'WCL proteins'
y_wcl <- filter_na(yeast_norm2, op = "<=", 
                   pat = "W", val = 2)

@@

# filter for proteins identified in min 1/5 reps of EV
# define 'EV proteins'
b_ev <- filter_na(biofilm_norm, op = "<=", 
                  pat = "EV", val = 4)

# filter for proteins identified in min 1/5 reps of WCL
# define 'WCL proteins'
b_wcl <- filter_na(biofilm_norm, op = "<=", 
                   pat = "W", val = 4)

@@

```{r atcc, include=FALSE}
# filter out reverse, contaminant proteins, proteins with <2 unique peptides
# extract LFQ intensity columns and UniProt accessions 
# log2 transform LFQ intensities
atcc_lfq <- atcc %>% 
  filter(Reverse != "+", 
         Potential.contaminant != "+", 
         Unique.peptides >= 2) %>% 
  convert_lfq(., atcc_exp)

@@

# normalise LFQ intensities
atcc_norm <- normalizeCyclicLoess(atcc_filt)

# filter for proteins identified in min 1/3 reps of 10231 EV
# define 'ATCC10231 EV proteins'
atcc1_ev <- filter_na(atcc_norm, op = "<=", 
                      pat = "A10231_EV", val = 2)

# filter for proteins identified in min 1/3 reps of 10231 WCL
# define 'ATCC10231 WCL proteins'
atcc1_w <- filter_na(atcc_norm, op = "<=", 
                     pat = "A10231_W", val = 2)

# filter for proteins identified in min 1/3 reps of 90028 EV
# define 'ATCC90028 EV proteins'
atcc9_ev <- filter_na(atcc_norm, op = "<=", 
                      pat = "A90028_EV", val = 2)

# filter for proteins identified in min 1/3 reps of 90028 WCL
# define 'ATCC90028 WCL proteins'
atcc9_w <- filter_na(atcc_norm, op = "<=", 
                      pat = "A90028_W", val = 2)

# can't impute with so many missing values
# filter for exclusive to 10231 EV or WCL or 90028 EV or WCL (don't impute)
atcc_excl <- filter_na4(atcc_norm, logic = "or", op = "==", 
                        pat1 = "A10231_EV", val1 = 3, 
                        pat2 = "A10231_W", val2 = 3, 
                        pat3 = "A90028_EV", val3 = 3, 
                        pat4 = "A90028_W", val4 = 3)

# filter for proteins with min 1 valid value in all 4 sample types (impute)
atcc_both <- filter_na4(atcc_norm, logic = "and", op = "<=", 
                        pat1 = "A10231_EV", val1 = 2, 
                        pat2 = "A10231_W", val2 = 2, 
                        pat3 = "A90028_EV", val3 = 2, 
                        pat4 = "A90028_W", val4 = 2)

# proteins with missing values tend to have lower intensity
# therefore proteins are MNAR, close to detection limit
# use left censored imputation method
atcc_imp <- impute_QRILC(atcc_both)

# recombine imputed proteins and non-imputed proteins in matrix
atcc_de <- rbind(atcc_excl, atcc_imp)
colnames(atcc_de) <- stringi::stri_replace_all_regex(colnames(atcc_de), 
                                                     c("A10231_", "A90028_"), 
                                                     c("A1_", "A9_"), 
                                                     vectorize_all = FALSE)

# see limma user guide section 9.2 for more info about DE
# create design matrix
atcc_samp <- data.frame(T = rep(c("A1_EV", "A1_WCL", 
                                  "A9_EV", "A9_WCL"), each = 3))

atcc_design <- stats::model.matrix(~ 0 + T, data = atcc_samp)
colnames(atcc_design) <- c("A1_EV", "A1_W", "A9_EV", "A9_W")

# define sample comparisons of interest
atcc_contrasts <- c("A1_EV - A1_W", "A9_EV - A9_W")

# make all pair-wise comparisons for specified contrasts
# and perform limma::eBayes()
atcc_efit <- limma_eBayes(atcc_de, atcc_design, atcc_contrasts)

# extract overall results
atcc_overall <- get_results(efit = atcc_efit, mat = atcc_de, 
                            p_val = 0.01, lfc = 0, type = "overall")

# extract results for ATCC strains
a1_res <- get_results(efit = atcc_efit, 
                      mat = atcc_de, 
                      p_val = 0.01, 
                      lfc = 0, 
                      type = "individual")[[1]]

a9_res <- get_results(efit = atcc_efit, 
                      mat = atcc_de, 
                      p_val = 0.01, 
                      lfc = 0, 
                      type = "individual")[[2]]
```

@@

# add proper protein functions to table 1
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
marker_longlist <- marker_longlist %>% 
  mutate(Function = function_desc1, 
         VDM = c("Y", rep("",3), rep("Y", 2), "", "Y", rep("", 8), rep("Y", 2), 
                 rep("", 4), rep("Y", 3), rep("", 2), rep("Y", 2), rep("", 5), 
                 "Y", rep("", 7), "Y"), 
         pack_row = c(4, rep(1,3), rep(4,2), 1, 2, rep(1,3), rep(1,3), 3, 2, 
                      rep(4,2), 1, rep(2,2), 3, 1, rep(4,2), 1, rep(4,3), 1, 
                      3, rep(1,3), 4, 1, 1, 2, 1, 2, 2, 2, 4)) %>% 
  arrange(pack_row)

# fix number of TM domains for CDR1;CDR2
marker_longlist[2, 7] <- "12;12"

# UniProt says SUR7 has 3 TM domains and a signal peptide
# much of literature says SUR7 has 4 TM domains
# TOPCONS2 predicts SUR7 has 4 TM domains and no signal peptide
# fix SUR7 entries
marker_longlist[19, 7] <- "4"
marker_longlist[19, 8] <- ""
```

@@

# draw table 1
knitr::kable(marker_longlist[ ,-10],
             caption = tab1_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE)  %>% 
  row_spec(row = c(1, 5, 6, 11, 12, 15:20, 22:27, 39), underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 20) %>% 
  pack_rows("Golgi, ER, vacuole", 21, 28) %>% 
  pack_rows("Mitochondria", 29, 31) %>% 
  pack_rows("Cell wall, cell surface", 32, 43) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} ortholog as 
                         annotated in the Candida Genome Database 
                        (ref:footnote1)", 
                        "Protein localisation was predicted using DeepLoc-1.0 
                        (ref:footnote2)", 
                        "Presence of transmembrane domains and absense of a 
                        signal peptide was predicted using TOPCONS2 
                        (ref:footnote3)"), 
           escape = FALSE, 
           threeparttable = TRUE)
```

@@

```{r figure2A9, include=FALSE}
# compare ATCC90028 EV WCL proteins
f2a2 <- plot_venn(list("EV" = atcc9_ev, "WCL" = atcc9_w), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans",
                  cex = 0.8,
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.55)), 
                  ext.percent = c(30,10,0),
                  ext.pos = c(45,315),
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

@@

# generate volcano plot
f2b2 <- plot_volcano(data = a9_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (99)", "WCL enriched (130)", 
                                 "Not significant (744)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC90028')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('99')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('130')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('744')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure2A1, include=FALSE}
# compare ATCC10231 EV WCL proteins
f2a3 <- plot_venn(list("EV" = atcc1_ev, "WCL" = atcc1_w), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8,
                  cat.fontfamily = "sans",
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  ext.percent = c(0,20,0),
                  ext.pos = 45,
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

@@

# generate volcano plot
f2b3 <- plot_volcano(data = a1_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (108)", "WCL enriched (142)", 
                                 "Not significant (435)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC10231')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('106')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('134')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('445')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

@@

```{r figure3Data, include=FALSE}
# get list of DAY286 yeast EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f3_y_go <- marker_comp[1] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  gsub("CHS3", "CaO19.4937", .) %>% 
  gsub("PEP1", "CaO19.3767", .)

# get list of DAY286 biofilm EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f3_b_go <- marker_comp[2] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017"), 
                                  vectorize_all = FALSE)

# get list of ATCC90028 EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f3_a9_go <- marker_comp[3] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5", "^MNN2$", 
                                    "MNN22", "MNN24", "ECM331", 
                                    "CAM1-1", "FCY21"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017", "CaO19.2347", 
                                    "CaO19.3803", "CaO19.1995", "CaO19.4255", 
                                    "CaO19.2651", "CaO19.8937"), 
                                  vectorize_all = FALSE)
f3_a9_go <- f3_a9_go[!f3_a9_go %in% c("orf19.7397.1", "orf19.7398")]

# get list of ATCC10231 EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f3_a1_go <- marker_comp[4] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5", "^MNN2$", 
                                    "MNN22", "MNN24", "ECM331", 
                                    "CAM1-1"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017", "CaO19.2347", 
                                    "CaO19.3803", "CaO19.1995", "CaO19.4255", 
                                    "CaO19.2651"), 
                                  vectorize_all = FALSE)
```

@@

f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:4, 35,37:38,42, 55:56,58:59), f3_pal) + 
  annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)

f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 63,65:67, 88:91), f3_pal) + 
  annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)
```

@@

```{r figure4Data, include=FALSE}
# figure 4a EV venn
f4a_comp <- list("DAY Y" = rownames(y_ev), 
                 "DAY B" = rownames(b_ev),
                 "ATCC90028" = rownames(atcc9_ev), 
                 "ATCC10231" = rownames(atcc1_ev))
f4a_comp <- lapply(f4a_comp, function(x) match_id(x, ref = uniprot, 
                                                  match = "UP_accession", 
                                                  new = "CGD_gene_name"))

@@

f4a_overlap <- plot_venn(vlist = f4a_comp, 
                         use_uniprot = FALSE, type = "df") %>% 
  filter(..count.. == 403) %>% 
  pull(..values..) %>% 
  unlist()

# figure 4b WCL venn
f4b_comp <- list("DAY Y" = rownames(y_wcl), 
                 "DAY B" = rownames(b_wcl),
                 "ATCC90028" = rownames(atcc9_w), 
                 "ATCC10231" = rownames(atcc1_w))
f4b_comp <- lapply(f4b_comp, function(x) match_id(x, ref = uniprot, 
                                                  match = "UP_accession", 
                                                  new = "CGD_gene_name"))

@@

# MDS data table
mds_data <- cbind(atcc_de, 
                  biofilm_de[match(rownames(atcc_de), rownames(biofilm_de)), ])

mds_data <- cbind(mds_data, 
                  yeast_de[match(rownames(mds_data), rownames(yeast_de)), ])

@@

# figure 4c MDS [dim1, dim2]
f4c <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(1,2)) + 
  scale_x_continuous(limits = c(-1.5, 2.5), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-1.5, 2.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(3, 2, 4, 1)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical") + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 1") + 
  ylab(label = "Dimension 2")

>>>>

# filter for proteins quantified in min 1/3 reps of EV
# define 'EV proteins'
y_ev <- filter_na(yeast_norm2, op = "<=", 
                  pat = "EV", val = 2)

# filter for proteins quantified in min 1/3 reps of WCL
# define 'WCL proteins'
y_wcl <- filter_na(yeast_norm2, op = "<=", 
                   pat = "W", val = 2)

@@

# filter for proteins quantified in min 1/5 reps of EV
# define 'EV proteins'
b_ev <- filter_na(biofilm_norm, op = "<=", 
                  pat = "EV", val = 4)

# filter for proteins quantified in min 1/5 reps of WCL
# define 'WCL proteins'
b_wcl <- filter_na(biofilm_norm, op = "<=", 
                   pat = "W", val = 4)

@@

```{r atccBoth, include=FALSE}
# filter out reverse, contaminant proteins, proteins with <2 unique peptides
# extract LFQ intensity columns and UniProt accessions 
# log2 transform LFQ intensities
atcc_lfq <- atcc %>% 
  filter(Reverse != "+", 
         Potential.contaminant != "+", 
         Unique.peptides >= 2) %>% 
  convert_lfq(., atcc_exp)

@@

# normalise LFQ intensities
atcc_norm <- normalizeCyclicLoess(atcc_filt)
```

```{r atcc1, include=FALSE}
# filter for proteins quantified in min 2/3 reps of EV or WCL
a1_norm <- filter_na2(atcc_norm, logic = "or", op = "<=", 
                      pat1 = "A10231_EV", val1 = 1, 
                      pat2 = "A10231_W", val2 = 1)
a1_norm <- a1_norm[, -c(7:12)]

# filter for proteins quantified in min 1/3 reps of EV
# define 'EV proteins'
a1_ev <- filter_na(a1_norm, op = "<=", pat = "EV", val = 2)

# filter for proteins quantified in min 1/3 reps of WCL
# define 'WCL proteins'
a1_wcl <- filter_na(a1_norm, op = "<=", pat = "W", val = 2)

# can't impute with so many missing values
# separate EV/WCL exclusive proteins (don't impute) from
# EV/WCL common proteins (impute)
a1_excl <- filter_na2(a1_norm, logic = "or", op = "==",
                      pat1 = "EV", val1 = 3,
                      pat2 = "W", val2 = 3)

a1_both <- filter_na2(a1_norm, logic = "and", op = "<=",
                      pat1 = "EV", val1 = 2,
                      pat2 = "W", val2 = 2)

# proteins with missing values tend to have lower intensity
# therefore proteins are MNAR, close to detection limit
# use left censored imputation method
a1_imp <- impute_QRILC(a1_both)

# recombine imputed proteins and non-imputed proteins in matrix
a1_de <- rbind(a1_excl, a1_imp)
colnames(a1_de) <- gsub("A10231", "A1", colnames(a1_de))

# see limma user guide section 9.2 for more info about DE
# create design matrix
a1_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 3)))

a1_design <- stats::model.matrix(~ 0 + T, data = a1_samp)
colnames(a1_design) <- c("A1_EV", "A1_W")

# define sample comparisons of interest
a1_contrasts <- c("A1_EV - A1_W")

# make all pair-wise comparisons between EV and WCL
# and perform limma::eBayes()
a1_efit <- limma_eBayes(a1_de, design = a1_design, contrasts = a1_contrasts)

# extract DE results
a1_res <- get_results(efit = a1_efit,
                      mat = a1_de,
                      p_val = 0.01,
                      lfc = 0,
                      type = "individual")[[1]]
```

```{r atcc9, include=FALSE}
# filter for proteins quantified in min 2/3 reps of EV or WCL
a9_norm <- filter_na2(atcc_norm, logic = "or", op = "<=",
                      pat1 = "A90028_EV", val1 = 1,
                      pat2 = "A90028_W", val2 = 1)
a9_norm <- a9_norm[, -c(1:6)]

# filter for proteins quantified in min 1/3 reps of EV
# define 'EV proteins'
a9_ev <- filter_na(a9_norm, op = "<=", pat = "EV", val = 2)

# filter for proteins quantified in min 1/3 reps of WCL
# define 'WCL proteins'
a9_wcl <- filter_na(a9_norm, op = "<=", pat = "W", val = 2)

# can't impute with so many missing values
# separate EV/WCL exclusive proteins (don't impute) from
# EV/WCL common proteins (impute)
a9_excl <- filter_na2(a9_norm, logic = "or", op = "==",
                      pat1 = "EV", val1 = 3,
                      pat2 = "W", val2 = 3)

a9_both <- filter_na2(a9_norm, logic = "and", op = "<=",
                      pat1 = "EV", val1 = 2,
                      pat2 = "W", val2 = 2)

# proteins with missing values tend to have lower intensity
# therefore proteins are MNAR, close to detection limit
# use left censored imputation method
a9_imp <- impute_QRILC(a9_both)

# recombine imputed proteins and non-imputed proteins in matrix
a9_de <- rbind(a9_excl, a9_imp)
colnames(a9_de) <- gsub("A90028", "A9", colnames(a9_de))

# see limma user guide section 9.2 for more info about DE
# create design matrix
a9_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 3)))

a9_design <- stats::model.matrix(~ 0 + T, data = a9_samp)
colnames(a9_design) <- c("A9_EV", "A9_W")

# define sample comparisons of interest
a9_contrasts <- c("A9_EV - A9_W")

# make all pair-wise comparisons between EV and WCL
# and perform limma::eBayes()
a9_efit <- limma_eBayes(a9_de, design = a9_design, contrasts = a9_contrasts)

# extract DE results
a9_res <- get_results(efit = a9_efit,
                      mat = a9_de,
                      p_val = 0.01,
                      lfc = 0,
                      type = "individual")[[1]]
```

@@

# add proper protein functions to table 1
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
marker_longlist2 <- marker_longlist %>% 
  mutate(Function = function_desc1, 
         pack_row = c(4, rep(1, 3), rep(4, 2), 1, 2, rep(1, 6), 3, rep(4, 2),
                      1, rep(2, 3), 1, rep(4, 2), 1, rep(4, 3), 1, 3, 
                      rep(1, 3), 4, 1, 2, 1, 2, 4)) %>% 
  arrange(pack_row) %>% 
  mutate(VDS = c(rep("", 11), "Y", rep("", 7), "Y", rep("", 7), 
                 rep("Y", 7), "", rep("Y", 4)))

# fix number of TM domains for CDR1;CDR2
marker_longlist2[2, 7] <- "12;12"

# UniProt says SUR7 has 3 TM domains and a signal peptide
# much of literature says SUR7 has 4 TM domains
# TOPCONS2 predicts SUR7 has 4 TM domains and no signal peptide
# fix SUR7 entries
marker_longlist2[18, 7] <- "4"
marker_longlist2[18, 8] <- ""

# Change name of orf19.6741 to Evp1
marker_longlist2[12, 1] <- paste0("EVP1",
                                  footnote_marker_alphabet(4))
```

@@

# draw table 1
knitr::kable(marker_longlist2[ ,-9],
             caption = tab1_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE)  %>% 
  row_spec(row = c(1, 5, 11, 12, 15:19, 21:25, 35), underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 19) %>% 
  pack_rows("Golgi, ER, vacuole", 20, 25) %>% 
  pack_rows("Mitochondria", 26, 27) %>% 
  pack_rows("Cell wall, cell surface", 28, 39) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} ortholog as 
                         annotated in the Candida Genome Database 
                        (ref:footnote1).", 
                        "Protein localisation was predicted using DeepLoc-1.0 
                        (ref:footnote2).", 
                        "Presence of transmembrane domains and absense of a 
                        signal peptide was predicted using TOPCONS2 
                        (ref:footnote3).",
                        "The name Evp1 for the protein encoded by orf19.6741 
                        was proposed in the present study."), 
           escape = FALSE, 
           threeparttable = TRUE)
```

@@

```{r figure2A9, include=FALSE}
# compare ATCC90028 EV WCL proteins
f2a2 <- plot_venn(list("EV" = a9_ev, "WCL" = a9_wcl), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans",
                  cex = 0.8,
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.55)), 
                  ext.percent = c(30,10,0),
                  ext.pos = c(45,315),
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

@@

# generate volcano plot
f2b2 <- plot_volcano(data = a9_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (86)", "WCL enriched (122)", 
                                 "Not significant (761)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC90028')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('86')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('122')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('761')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure2A1, include=FALSE}
# compare ATCC10231 EV WCL proteins
f2a3 <- plot_venn(list("EV" = a1_ev, "WCL" = a1_wcl), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8,
                  cat.fontfamily = "sans",
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  ext.percent = c(0,20,0),
                  ext.pos = 45,
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

@@

# generate volcano plot
f2b3 <- plot_volcano(data = a1_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (55)", "WCL enriched (52)", 
                                 "Not significant (567)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC10231')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('55')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('52')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('567')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

@@

```{r figure3Data, include=FALSE}
# get list of DAY286 yeast EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f3_y_go <- marker_comp[1] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  gsub("CHS3", "CaO19.4937", .) %>% 
  gsub("PEP1", "CaO19.3767", .)
# paste into FungiFun2 and download results .csv

# get list of DAY286 biofilm EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f3_b_go <- marker_comp[2] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017"), 
                                  vectorize_all = FALSE)
# paste into FungiFun2 and download results .csv

# get list of ATCC90028 EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f3_a9_go <- marker_comp[3] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5", "^MNN2$", 
                                    "MNN22", "MNN24", "ECM331", 
                                    "CAM1-1", "FCY21"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017", "CaO19.2347", 
                                    "CaO19.3803", "CaO19.1995", "CaO19.4255", 
                                    "CaO19.2651", "CaO19.8937"), 
                                  vectorize_all = FALSE)
f3_a9_go <- f3_a9_go[!f3_a9_go %in% c("orf19.7397.1", "orf19.7398")]
# paste into FungiFun2 and download results .csv

# get list of ATCC10231 EV proteins exclusive and sig. enriched
# substitute protein names that don't work with FungiFun2
f3_a1_go <- marker_comp[4] %>% 
  unlist() %>% 
  strsplit(., ";") %>% 
  unlist() %>% 
  stringi::stri_replace_all_regex(., 
                                  c("CHS3", "PEP1", "ALS3", 
                                    "PLB3", "PLB4.5", "^MNN2$", 
                                    "MNN22", "MNN24", "ECM331", 
                                    "CAM1-1"), 
                                  c("CaO19.4937", "CaO19.3767", "CaO19.1816",
                                    "CaO19.6594", "CaO19.9017", "CaO19.2347", 
                                    "CaO19.3803", "CaO19.1995", "CaO19.4255", 
                                    "CaO19.2651"), 
                                  vectorize_all = FALSE)
# paste into FungiFun2 and download results .csv
```

@@

f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:3,6, 27,29,32:33, 46,49,51:52), f3_pal) + 
  annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)

f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 62,64:66, 86:89), f3_pal) + 
  annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)
```

@@

```{r figure4Data, include=FALSE}
# figure 4a EV venn
f4a_comp <- list("DAY Y" = rownames(y_ev), 
                 "DAY B" = rownames(b_ev),
                 "ATCC90028" = rownames(a9_ev), 
                 "ATCC10231" = rownames(a1_ev))
f4a_comp <- lapply(f4a_comp, function(x) match_id(x, ref = uniprot, 
                                                  match = "UP_accession", 
                                                  new = "CGD_gene_name"))

@@

f4a_overlap <- plot_venn(vlist = f4a_comp, 
                         use_uniprot = FALSE, type = "df") %>% 
  filter(..count.. == 396) %>% 
  pull(..values..) %>% 
  unlist()

# figure 4b WCL venn
f4b_comp <- list("DAY Y" = rownames(y_wcl), 
                 "DAY B" = rownames(b_wcl),
                 "ATCC90028" = rownames(a9_wcl), 
                 "ATCC10231" = rownames(a1_wcl))
f4b_comp <- lapply(f4b_comp, function(x) match_id(x, ref = uniprot, 
                                                  match = "UP_accession", 
                                                  new = "CGD_gene_name"))

@@

# MDS data table
mds_a9 <- a9_de %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column(var = "id")

mds_a1 <- a1_de %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column(var = "id")

mds_biofilm <- biofilm_de%>% 
  as.data.frame() %>% 
  tibble::rownames_to_column(var = "id")

mds_yeast <- yeast_de%>% 
  as.data.frame() %>% 
  tibble::rownames_to_column(var = "id")

mds_data <- full_join(mds_a9, mds_a1, by = "id") %>% 
  full_join(., mds_biofilm, by = "id") %>% 
  full_join(., mds_yeast, by = "id") %>% 
  tibble::column_to_rownames(var = "id")

@@

# figure 4c MDS [dim1, dim2]
f4c <- plot_mds(mds_data, mat_labels = mds_labels, 
                shape_size = 3, dim.plot = c(1,2)) + 
  scale_x_continuous(limits = c(-1.5, 2.5), 
                     expand = c(0,0)) + 
  scale_y_continuous(limits = c(-2.5, 1.5), 
                     expand = c(0,0)) + 
  scale_fill_manual(breaks = c("Y", "A9", "A1", "B"), 
                    values = st_pal[c(3, 2, 4, 1)], 
                    labels = c("DAY Y", "A90028", "A10231", "DAY B"), 
                    guide = "legend") + 
  scale_shape_manual(values = c(22,24)) + 
  theme_bw() + 
  theme(legend.title = element_blank(),
        legend.position = "right", 
        legend.text = element_text(size = 8), 
        legend.direction = "vertical") + 
  guides(fill = guide_legend(override.aes = list(shape = 21))) + 
  xlab(label = "Dimension 1") + 
  ylab(label = "Dimension 2")
